Performance Models for Data Transfers: A Case Study with Molecular Chemistry Kernels

### 2019-04-03 Article/article.tex
rewritten infinite memory proof

\newcommand{\hp}{{\sc HeteroPrio}\xspace}
\SetKw{continue}{continue}

@@

@@

	\todo[inline]{SKumar: Modify both proofs }
	\section{Data Transfer problem formulation}
%%	\section*{Order of data transfers}

	To exploit the full potential of a system tasks may get scheduled on processing
	units where all of their data does not reside. A task may require all of its data
	in local memory before starting the execution. There may be multiple tasks
	scheduled on a processing unit, which require to transfer data from the same
	memory node. Order of data transfers for such tasks is very crucial for the
	communication-computation overlap, thus for the overall performance. Tasks may
	also produce some output data, which, in general, is very less.  It is often the case that future tasks running on the same memory node require output data of the past tasks. Therefore, most runtime systems transfer data to other memory nodes based on the demand -- not immediately. It is possible that all output data can be stored in a preallocated separate buffer on a memory node. Hence, we do not consider output data separately in our analysis and assume that output data is negligible (zero or stored in a separate buffer) for each task. We prove that order of execution of such tasks with finite memory capacity, is an NP-complete problem.

	\subsection{Infinite Memory Case}
	Let $S$ be the set of tasks assigned on processor $P$ with memory unit $M$, and this set of tasks  need input data from another memory unit $M'$. We assume that size of $M$ is very large and there will not be any memory capacity restriction for tasks.

	\begin{algorithm}
	\caption{\label{alg:OrderOfExecutionInfinteMemory}Algorithm to determine the order of processing for a set of ready tasks (infinite memory case)}
	\begin{algorithmic}[1]
		\STATE Divide ready tasks in two sets $S_1$ and $S_2$. If computation time of a task $T$is not less than its communication time, then $T$ is in $S_1$ otherwise $S_2$.
		\STATE Sort $S_1$ in queue $Q_1$ by non-decreasing communication times
		\STATE Sort $S_2$ in queue $Q_2$ by non-increasing computation times
		\WHILE{all tasks did not complete}
		\IF{$Q_1 \neq \emptyset$}
		\STATE remove a task $T$ from beginning of $Q_1$ for processing
		\ELSE 
		\STATE remove a task $T$ from beginning of $Q_2$ for processing
		\ENDIF
		\ENDWHILE
	\end{algorithmic}
\end{algorithm}

	\noindent \textbf{Claim} : Order provided by Algorithm~\ref{alg:OrderOfExecutionInfinteMemory} achives the optimal makespan for a set of ready tasks.
	\todo[inline]{SKumar:rewrite this proof}
	\begin{proof}
		Let us first define some notations which we need for this proof.
%%		\todo[inline]{SKumar: Specify the destination for all notations}
		\begin{align*}
		t : & \text{Time at which data transfer for task A starts in original schedule}\\
		S_A : & \text{ Start of computation  time of task A in original schedule}\\
		S_B : & \text{ Start of computation time of task B in original schedule}\\
		S'_A : & \text{ Start of computation time of task A in swapped schedule}\\
		S'_B : & \text{ Start of computation time of task B in swapped schedule}\\
		CM(A) : & \text{ Data transfer time for task A}\\
		CM(B) : & \text{ Data transfer time for task B}\\
		CP(A) : & \text{ Computation time of of task A}\\
		CP(B) : & \text{ Computation time of task B}\\
		\rho : & \text{ ratio of length of task and data transfer time}
		\end{align*}
	\end{proof}

	Let $S$ be the schedule obtained by the above heuristic and $O$ be an optimal schedule. We prove the above claim by converting $S$ to $O$ and showing that at each step completing time of intermediate schedule is not less than the completion time of original schedule $S$. In order to do so, we make sure order of two tasks in both schedules $S$ and $O$ is same. If not, We perform swapping of two tasks.

	\noindent If we prove the swapping strategy for two contiguous tasks holds, then the same strategy transitively hold for any two tasks of Schedule $S$

	Let $A$ and $B$ are two contiguous tasks of schedule $S$, which need to be swapped.
	\todo[inline]{SKumar: draw an equivalent xfig diagram}
	\begin{figure}[htb]
		\centering
		\includegraphics[width=\textwidth, height=0.5\textheight, 
		keepaspectratio]{Figs/swappedSchedule.jpg}
		\caption{ \label{fig:bothSchedule} Original and Swapped Schedule}
	\end{figure}

	We can write the following constraints based on the two schedules of the Fig~\ref{fig:bothSchedule}.

	\begin{eqnarray*}
		S_A & = & max(CM(A), l) \\
		S_B & = & max(S_A + CP(A), CM(A) + CM(B))
	\end{eqnarray*}

	Completion time in original Schedule = $S_B + CP(B)$
	\begin{eqnarray*}
		S'_B & = & max(CM(B), l) \\
		S'_A & = & max(S'_B + CP(B), CM(A) + CM(B))
	\end{eqnarray*}

	Completion time in swapped Schedule = $S'_A + CP(A)$

	Our goal is to prove the following inequality.
	\begin{eqnarray*}
		S_B + CP(B) & \le & S'_A + CP(A)
	\end{eqnarray*}
	\begin{proof}
		\begin{eqnarray*}
			S_B + CP(B) & = & max(S_A + CP(A)+CP(B), CM(A) + CM(B) + CP(B))\\
			& = & max(CM(A) + CP(A) + CP(B), l+CP(A) + CP(B), CM(A) + CM(B) + CP(B)) 
		\end{eqnarray*}
		Case I: $A, B\in ST_1, CM(A) \le CM(B), CP(A) \ge CM(A), CP(B) \ge CM(B)$
		\begin{eqnarray*}
			S_B + CP(B) & = & max(CM(A) + CP(A) + CP(B), l+CP(A) + CP(B), CM(A) + CM(B) + CP(B)) \\
			& \le & max(CM(A) + CP(B), l+CP(B), CM(B)+CP(B)) + CP(A)\\
			& = & max(CM(B) + CP(B), l + CP(B)) + CP(A) \\
			& = & max(max(CM(B), l) + CP(B), CM(A) + CM(B)) + CP(A) \\
			& = & max(S'_B + CP(B), CM(A) +CM(B)) + CP(A) \\
			& = & S'_A + CP(A)
		\end{eqnarray*}
		Case II: $A, B\in ST_2, CP(A) \ge CP(B), CP(A) < CM(A), CP(B) < CM(B)$
		\begin{eqnarray*}
			S_B + CP(B) & = & max(CM(A) + CP(A) + CP(B), l+CP(A) + CP(B), CM(A) + CM(B) + CP(B)) \\
			& \le & max(CM(A) + CP(B), l+CP(B), CM(A)+CM(B)) + CP(A)\\
			& = & max(CM(A) + CM(B), l + CP(B)) + CP(A) \\
			& = & max(CM(B) + CP(B), l + CP(B), CM(A) + CM(B)) + CP(A) \\
			& = & max(max(CM(B), l) + CP(B), CM(A) + CM(B)) + CP(A) \\
			& = & max(S'_B + CP(B), CM(A) +CM(B)) + CP(A) \\
			& = & S'_A + CP(A)
		\end{eqnarray*}
		Case III: $A \in ST_1, B\in ST_2, CP(A) \ge CM(A), CP(B) < CM(B)$
		\begin{eqnarray*}
			S_B + CP(B) & = & max(CM(A) + CP(A) + CP(B), l+CP(A) + CP(B), CM(A) + CM(B) + CP(B)) \\
			& \le & max(CM(A) + CP(B), l + CP(B), CM(B) + CP(B)) + CP(A)\\
			& \le & max(CM(A) + CM(B), l + CP(B), CM(B) + CP(B)) + CP(A) \\
			& = & max(max(CM(B), l) + CP(B), CM(A) + CM(B)) + CP(A) \\
			& = & max(S'_B + CP(B), CM(A) +CM(B)) + CP(A) \\
			& = & S'_A + CP(A)
		\end{eqnarray*}
	\end{proof}

This problem can be expressed as 2-machine flowshop problem with infinite storage, where communication time is the processing time on first machine and computation time is the processing time on second machine and the goal is to minimize the overall makespan. In ~\cite{GareyJohnson}, Johnson's algorithm also achieves the optimal makespan but the proof techniques and algorithm are quite different from ours.
	\subsection{Finite Memory}

>>>>

\SetKw{continue}{continue}

@@

\definecolor{pdfurlcolor}{rgb}{0,0,0.6}
\definecolor{pdfcitecolor}{rgb}{0,0.6,0}
\definecolor{pdflinkcolor}{rgb}{0.6,0,0}
\usepackage{epsfig,color}
%\usepackage[colorlinks=true,citecolor=pdfcitecolor,urlcolor=pdfurlcolor,linkcolor=pdflinkcolor,pdfborder={0 0 0}]{hyperref}

\newcommand{\scomm}{\ensuremath{{\cal S}_{\text{COMM}}}}
\newcommand{\scomp}{\ensuremath{{\cal S}_{\text{COMP}}}}

%%\newtheorem{theorem}{Theorem}
%%\newtheorem{corollary}{Corollary}[theorem]
%\newtheorem{lemma}[theorem]{Lemma}

@@

%%	\todo[inline]{SKumar: Modify both proofs }
	\section{Data Transfer problem formulation}
%%	\section*{Order of data transfers}

	To exploit the full potential of a system tasks may get scheduled on processing
	units where all of their data does not reside. A task may require all of its data
	in local memory before starting the execution. There may be multiple tasks
	scheduled on a processing unit, which require to transfer data from the same
	memory node. Order of data transfers for such tasks is very crucial for the
	communication-computation overlap, thus for the overall performance. Tasks may
	also produce some output data, which, in general, is very less.  It is often the case that future tasks running on the same memory node require output data of the past tasks. Therefore, most runtime systems transfer data to other memory nodes based on the demand -- not immediately. It is possible that all output data can be stored in a preallocated separate buffer on a memory node. Hence, we do not consider output data separately in our analysis and assume that output data is negligible (zero or stored in a separate buffer) for each task. We prove that order of execution of such tasks with finite memory capacity, is an NP-complete problem. We also present an optimal algorithm to determine the order of execution of tasks when there is not any  restriction on memory limit.

	\subsection{Infinite Memory Case}
	Let $S$ be the set of tasks assigned on a processor with memory unit $M$, and this set of tasks  need input data from another memory unit $M'$. We assume that size of $M$ is very large and there will not be any memory capacity restriction for tasks.

	Let \scomm($i$) and  \scomp($i$) represent the start times of task $i$ on communication and computation resources. $CM_i$ and $CP_i$ are communication and computation times of task $i$.

	\begin{algorithm}
	\caption{\label{alg:OrderOfExecutionInfinteMemory}Algorithm to determine the order of processing and schedule for a set of ready tasks (infinite memory case)}
	\begin{algorithmic}[1]
		\STATE Divide ready tasks in two sets $S_1$ and $S_2$. If computation time of a task $T$is not less than its communication time, then $T$ is in $S_1$ otherwise $S_2$.
		\STATE Sort $S_1$ in queue $Q_1$ by non-decreasing communication times
		\STATE Sort $S_2$ in queue $Q_2$ by non-increasing computation times
		\STATE $Q \gets  Q_1$
		\STATE Append $Q_2$ to $Q$
		\STATE $early\_available\_time\_on\_communication\_resource \gets 0$
		\STATE $early\_available\_time\_on\_computation\_resource \gets 0$
		\WHILE{$Q \neq \emptyset$}
		\STATE remove a task $T$ from beginning of $Q$ for processing
		\STATE $\scomm(T) \gets  early\_available\_time\_on\_communication\_resource$
		\STATE $\scomp(T) \gets  max(\scomm(T) + CM_T, early\_available\_time\_on\_computation\_resource)$
		\STATE $early\_available\_time\_on\_communication\_resource \gets  \scomm(T) + CM_T$
		\STATE $early\_available\_time\_on\_computation\_resource \gets  \scomp(T) + CP_T$
		\ENDWHILE
	\end{algorithmic}
\end{algorithm}

%%	\noindent \textbf{Claim} : Order provided by Algorithm~\ref{alg:OrderOfExecutionInfinteMemory} achives the optimal makespan for a set of ready tasks.
%%	\todo[inline]{SKumar:rewrite this proof}
In order to prove the optimality of makespan for the schedule obtained by the above algorithm, we need the following lemma.

	\begin{lemma}\label{lemma:swappingOfTasks}
	Swapping two contiguous tasks $A$ and $B$ in a schedule does not improve the makespan if one of the conditions is true.
	\begin{enumerate}[label=\roman*)]
		\item  $CP_A \ge CM_A, CP_B \ge CM_B, CM_A \le CM_B$
		\item $CP_A < CM_A, CP_B < CM_B, CP_A \ge CP_B$
		\item $CP_A \ge CM_A, CP_B < CM_B$
	\end{enumerate}
\end{lemma}
\begin{proof}
	Let $t_1$ and $t_2$ be the early start time on communication and computation resources just before the task $A$ starts.

	\begin{figure}[htb]
		\centering
		\includegraphics[width=\textwidth, height=0.5\textheight, 
		keepaspectratio]{Figs/swappedSchedule.jpg}
		\caption{ \label{fig:bothSchedule} Original and Swapped Schedule}
	\end{figure}

	We write the following constraints based on the two schedules of the Fig~\ref{fig:bothSchedule}.

	\begin{eqnarray*}
		\scomp(A) & = & max(t_1 + CM_A, t_2) \\
		\scomp(B) & = & max(\scomp(A) + CP_A,  t_1 + CM_A + CM_B)
	\end{eqnarray*}

	Completion time of $B$ in original Schedule = $\scomm(B) + CP_B$

	\begin{eqnarray*}
		\text{Completion time of $B$ in swapped Schedule, } \scomp '(B) & = & max(t_1 + CM_B, t_2)\\
		\text{Completion time of $A$ in swapped Schedule, } \scomp '(A) & = & max(\scomp'(B) + CP_B, t_1 + CM_B + CM_A)
	\end{eqnarray*}

	In both schedules, early available time on communication resource after scheduling $A$ and $B$ is same. If we show that early available time on computation resource in swapped schedule after scheduling both tasks is not less than the time of original schedule, then we are done. Hence our goal is to prove that,		
	$$\scomp(B) + CP_B \le \scomp'(A) + CP_A $$

	\begin{eqnarray*}
		\scomp(B) + CP_B & = & max(\scomp(A) + CP_A + CP_B,  t_1 + CM_A + CM_B + CP_B)\\
		& = & max(t_1 + CM_A + CP_A + CP_B, t_2 + CP_A + CP_B, t_1 + CM_A + CM_B + CP_B) 
	\end{eqnarray*}

	Case I: $CP_A \ge CM_A, CP_B \ge CM_B, CM_A \le CM_B$
	\begin{eqnarray*}
		\scomp(B) + CP_B & = & max(t_1 + CM_A + CP_A + CP_B, t_2 + CP_A + CP_B, t_1 + CM_A + CM_B + CP_B)\\
		& \le& max(t_1 + CM_A + CP_B, t_2  + CP_B, t_1  + CM_B + CP_B) + CP_A\\
		& = & max( t_1  + CM_B + CP_B, t_2  + CP_B) + CP_A \\
		& = & max(max(t_1 + CM_B, t_2) + CP_B, t_1 + CM_A + CM_B) + CP_A\\
		& = & max(\scomp'(B) + CP_B, t_1 + CM_A + CM_B) + CP_A \\
		& = & \scomp'(A) + CP_A
	\end{eqnarray*}
	Case II: $CP_A < CM_A, CP_B < CM_B, CP_A \ge CP_B$
	\begin{eqnarray*}
		\scomp(B) + CP_B & = & max(t_1 + CM_A + CP_A + CP_B, t_2 + CP_A + CP_B, t_1 + CM_A + CM_B + CP_B)\\
		& \le & max(t_1 + CM_A + CP_B, t_2+CP_B, t_1 + CM_A + CM_B) + CP_A\\
		& = & max(t_1 + CM_A + CM_B, t_2+ CP_B) + CP_A \\
		& = & max(t_1 + CM_B + CP_B, t_2 + CP_B, t_1 + CM(A) + CM_B) + CP_A \\
		& = & max(max(t_1 + CM_B, t_2) + CP_B, t_1 + CM_A + CM_B) + CP_A \\
		& = & max(\scomp'(B) + CP_B, t_1 + CM_A +CM_B) + CP_A \\
		& = & \scomp'(A) + CP_A
	\end{eqnarray*}
	Case III: $CP_A \ge CM_A, CP_B < CM_B$
	\begin{eqnarray*}
		\scomp(B) + CP_B & = & max(t_1 + CM_A + CP_A + CP_B, t_2 + CP_A + CP_B, t_1 + CM_A + CM_B + CP_B)\\
		& \le & max(t_1 + CM_A + CP_B, t_2 + CP_B, t_1 + CM_B + CP_B) + CP_A\\
		& \le & max(t_1 + CM_A + CM_B, t_2 + CP_B, t_1 + CM_B + CP_B) + CP_A \\
		& = & max(max(t_1 + CM_B, t_2) + CP_B, t_1 + CM_A + CM_B) + CP_A \\
		& = & max(\scomp'(B) + CP_B, t_1 + CM_A +CM_B) + CP_A \\
		& = & \scomp'(A) + CP_A
	\end{eqnarray*}
\end{proof}

\begin{theorem}
	Scheduled constructed by Algorithm~\ref{alg:OrderOfExecutionInfinteMemory} achieves optimal makespan.
\end{theorem}
%%	\begin{proof}
%%		Let us first define some notations which we need for this proof.
%%%%		\todo[inline]{SKumar: Specify the destination for all notations}
%%		\begin{align*}
%%		t : & \text{Time at which data transfer for task A starts in original schedule}\\
%%		S_A : & \text{ Start of computation  time of task A in original schedule}\\
%%		S_B : & \text{ Start of computation time of task B in original schedule}\\
%%		S'_A : & \text{ Start of computation time of task A in swapped schedule}\\
%%		S'_B : & \text{ Start of computation time of task B in swapped schedule}\\
%%		CM(A) : & \text{ Data transfer time for task A}\\
%%		CM(B) : & \text{ Data transfer time for task B}\\
%%		CP(A) : & \text{ Computation time of of task A}\\
%%		CP(B) : & \text{ Computation time of task B}\\
%%		\rho : & \text{ ratio of length of task and data transfer time}
%%		\end{align*}
%%	\end{proof}

	\begin{proof}

	Let $O$ be an optimal schedule. We assume that order of communications and computations is same on both resources in $O$. If it is not the case, we make the order of computations same as the order of communications without increasing the makespan.  Suppose two tasks have opposite order on both resources then we position the second task just before the first task on the computation resource. It is evident that this change does not alter the optimal  makespan, we repeat this procedure until order of communications and computations is same in $O$.

	Let $S$ be the  schedule obtained from Algorithm~\ref{alg:OrderOfExecutionInfinteMemory}. We prove the theorem by converting $S$ to $O$ and showing that at each step makespan of intermediate schedule is not less than the original makespan. We rely on Lemma~\ref{lemma:swappingOfTasks} to convert $S$ to $O$.

  We traverse schedule $O$ from left to right and for each $ith$ task in sequence, we apply Lemma~\ref{lemma:swappingOfTasks} repetitively until order of task in the swapped schedule is same. It is obvious that after moving the $ith$ task at the beginning remaining schedule (schedule after $ith$ task) still satisfies one of the conditions of Lemma~\ref{lemma:swappingOfTasks}.

  Let the final swapped schedule is $S_{final}$. From Lemma~\ref{lemma:swappingOfTasks}, $makespan(S_{final}) \ge makesapn(S)$. From the construction, $makespan(S_{final}) \le makesapn(O)$. As $O$ is an optimal schedule, hence $makespan(S) = makesapn(O)$. This completes our proof.

%%	 
%%	Let $S$ be the schedule obtained by the above heuristic and $O$ be an optimal schedule. We prove the above claim by converting $S$ to $O$ and showing that at each step completing time of intermediate schedule is not less than the completion time of original schedule $S$. In order to do so, we make sure order of two tasks in both schedules $S$ and $O$ is same. If not, We perform swapping of two tasks.
%%	
%%	\noindent If we prove the swapping strategy for two contiguous tasks holds, then the same strategy transitively hold for any two tasks of Schedule $S$

%%	Let $A$ and $B$ are two contiguous tasks of schedule $S$, which need to be swapped.
%%	\todo[inline]{SKumar: draw an equivalent xfig diagram}
%%	\begin{figure}[htb]
%%		\centering
%%		\includegraphics[width=\textwidth, height=0.5\textheight, 
%%		keepaspectratio]{Figs/swappedSchedule.jpg}
%%		\caption{ \label{fig:bothSchedule} Original and Swapped Schedule}
%%	\end{figure}
%%	
%%	We can write the following constraints based on the two schedules of the Fig~\ref{fig:bothSchedule}.
%%	
%%	\begin{eqnarray*}
%%		S_A & = & max(CM(A), l) \\
%%		S_B & = & max(S_A + CP(A), CM(A) + CM(B))
%%	\end{eqnarray*}
%%	
%%	Completion time in original Schedule = $S_B + CP(B)$
%%	\begin{eqnarray*}
%%		S'_B & = & max(CM(B), l) \\
%%		S'_A & = & max(S'_B + CP(B), CM(A) + CM(B))
%%	\end{eqnarray*}
%%	
%%	Completion time in swapped Schedule = $S'_A + CP(A)$
%%	
%%	Our goal is to prove the following inequality.
%%	\begin{eqnarray*}
%%		S_B + CP(B) & \le & S'_A + CP(A)
%%	\end{eqnarray*}
%%	\begin{proof}
%%		\begin{eqnarray*}
%%			S_B + CP(B) & = & max(S_A + CP(A)+CP(B), CM(A) + CM(B) + CP(B))\\
%%			& = & max(CM(A) + CP(A) + CP(B), l+CP(A) + CP(B), CM(A) + CM(B) + CP(B)) 
%%		\end{eqnarray*}
%%		Case I: $A, B\in ST_1, CM(A) \le CM(B), CP(A) \ge CM(A), CP(B) \ge CM(B)$
%%		\begin{eqnarray*}
%%			S_B + CP(B) & = & max(CM(A) + CP(A) + CP(B), l+CP(A) + CP(B), CM(A) + CM(B) + CP(B)) \\
%%			& \le & max(CM(A) + CP(B), l+CP(B), CM(B)+CP(B)) + CP(A)\\
%%			& = & max(CM(B) + CP(B), l + CP(B)) + CP(A) \\
%%			& = & max(max(CM(B), l) + CP(B), CM(A) + CM(B)) + CP(A) \\
%%			& = & max(S'_B + CP(B), CM(A) +CM(B)) + CP(A) \\
%%			& = & S'_A + CP(A)
%%		\end{eqnarray*}
%%		Case II: $A, B\in ST_2, CP(A) \ge CP(B), CP(A) < CM(A), CP(B) < CM(B)$
%%		\begin{eqnarray*}
%%			S_B + CP(B) & = & max(CM(A) + CP(A) + CP(B), l+CP(A) + CP(B), CM(A) + CM(B) + CP(B)) \\
%%			& \le & max(CM(A) + CP(B), l+CP(B), CM(A)+CM(B)) + CP(A)\\
%%			& = & max(CM(A) + CM(B), l + CP(B)) + CP(A) \\
%%			& = & max(CM(B) + CP(B), l + CP(B), CM(A) + CM(B)) + CP(A) \\
%%			& = & max(max(CM(B), l) + CP(B), CM(A) + CM(B)) + CP(A) \\
%%			& = & max(S'_B + CP(B), CM(A) +CM(B)) + CP(A) \\
%%			& = & S'_A + CP(A)
%%		\end{eqnarray*}
%%		Case III: $A \in ST_1, B\in ST_2, CP(A) \ge CM(A), CP(B) < CM(B)$
%%		\begin{eqnarray*}
%%			S_B + CP(B) & = & max(CM(A) + CP(A) + CP(B), l+CP(A) + CP(B), CM(A) + CM(B) + CP(B)) \\
%%			& \le & max(CM(A) + CP(B), l + CP(B), CM(B) + CP(B)) + CP(A)\\
%%			& \le & max(CM(A) + CM(B), l + CP(B), CM(B) + CP(B)) + CP(A) \\
%%			& = & max(max(CM(B), l) + CP(B), CM(A) + CM(B)) + CP(A) \\
%%			& = & max(S'_B + CP(B), CM(A) +CM(B)) + CP(A) \\
%%			& = & S'_A + CP(A)
%%		\end{eqnarray*}
%%	\end{proof}

The problem considered here can also be expressed as 2-machine flowshop problem with infinite storage, where communication time is the processing time on first machine and computation time is the processing time on second machine and the goal is to minimize the overall makespan. In ~\cite{johnson}, Johnson's algorithm also achieves the optimal makespan but the proof techniques and algorithm are quite different from ours.
	\subsection{Finite Memory}
